Hierarchical Dispatching and Overriding

### 2017-08-10 Aplas17/sections/Auxiliary.tex
revise full
added abstract method
canInstantiate

@@

\begin{figure*}[t]
    \centering
    \vspace{-1ex}
    \begin{tabular}{ccc}
        \includegraphics[width=2cm]{pics/p1.pdf}\hspace{4pt} &
        \includegraphics[width=2cm]{pics/p2.pdf}\hspace{4pt} &
        \includegraphics[width=2cm]{pics/p3.pdf}\hspace{4pt} \\
        (a) $\mbody(m,C,A) = (A,...)$\ \ \  & (b) $\mbody(m,C,A) = (C,...)$\ \ \  & (c) $\mbody(m,C,A) = (C,...)$
    \end{tabular} \\
   \begin{tabular}{cc}
    \includegraphics[height=3cm]{pics/p4.pdf}\hspace{4pt} &
    \includegraphics[height=3cm]{pics/p5.pdf}\hspace{4pt} \\ 
    (d) $\mbody(m,D,A) = \keyword{undefined}$\ \ \  & (e) $\mbody(m,D,A) = \keyword{undefined}$
   \end{tabular}
    \caption{Examples on $\mbody$. ``$\uparrow$'' stands for hierarchical overriding.}\label{fig:examplesmbody}
    %\saveSpaceFig
\end{figure*}

@@

@@

To calculate $\mbody(m, I_d, I_s)$:
\begin{itemize}
    \item First, it invokes $\mostSpecific(m, I_d, I_s)$ and returns a set.
    \item If $\mostSpecific$ returns a singleton set $\{I\}$, then it is good, otherwise, $\mbody$ is undefined in
    this case. The set $\{I\}$ implies that we will use the $m$ from $I$ without ambiguity. Moreover, we have to invoke $\mostSpecificOverride(m, I_d, I)$, to check if there are updated versions of $m$ between $I_d$ and $I$. Again we forbid ambiguity, so the expected set after pruning is also a singleton set $\{J\}$.
    \item Finally, we fetch the implementation of $m$ in interface $J$ and return its related information.
\end{itemize}
The definition of $\mtype$ used in typing rules simply relies on $\mbody$. In short,
$$\mbody(m, I, I) = (J, \overline{I_x}\ \overline{x}, I_e\ e) \ \Longrightarrow\ \mtype(m, I) = \overline{I_x}\rightarrow I_e$$

>>>>

    \inferrule* [left=]
        {  \mostSpecific(m, I_d, I_s) = \{I\} \\
            \mostSpecificOverride(m, I_d, I) = \{J\} \\
            \kwinterface \; J \; \kwextends \; \overline{J} \; \{\absmethod{I_e}{m}{I_x}{x}{I}\}}
        {\mbody(m, I_d, I_s) = (J, \overline{I_x} \; \overline{x}, I_e \; \o)}

@@

\begin{figure*}[t]
    \centering
    \vspace{-1ex}
    \begin{tabular}{ccc}
        \includegraphics[width=1.5cm]{pics/p1.pdf}\hspace{4pt} &
        \includegraphics[width=1.5cm]{pics/p2.pdf}\hspace{4pt} &
        \includegraphics[width=1.5cm]{pics/p3.pdf}\hspace{4pt} \\
        (a) $\mbody(m,C,A) = (A,...)$\ \ \  & (b) $\mbody(m,C,A) = (C,...)$\ \ \  & (c) $\mbody(m,C,A) = (C,...)$
    \end{tabular} \\
   \begin{tabular}{cc}
    \includegraphics[height=3cm]{pics/p4.pdf}\hspace{4pt} &
    \includegraphics[height=3cm]{pics/p5.pdf}\hspace{4pt} \\ 
    (d) $\mbody(m,D,A) = \keyword{undefined}$\ \ \  & (e) $\mbody(m,D,A) = \keyword{undefined}$
   \end{tabular}
    \caption{Examples on $\mbody$. ``$\uparrow$'' stands for hierarchical overriding.}\label{fig:examplesmbody}
    %\saveSpaceFig
\end{figure*}

@@

\subsection{$\canInstantiate$}
We use the auxilary function $\canInstantiate(I)$ to check whether an interface $I$ can be instantiated or not.
The algorithm is decribed below:
\begin{enumerate}
\item Suppose $\mostSpecific(m, I, I) = \overline{J}$, where $\overline{J}$ is a list of interfaces.
\item If $\forall J_i \in \overline{J}, if \mostSpecificOverride(m, I, J_i) = \{ K \} $ and $m$ in $K$ is not abstract, 
then $\canInstantiate(I) = true$, else $\canInstantiate(I) = false$.
\end{enumerate}

@@

To calculate $\mbody(m, I_d, I_s)$:
\begin{itemize}
    \item First, it invokes $\mostSpecific(m, I_d, I_s)$ and returns a set.
    \item If $\mostSpecific$ returns a singleton set $\{I\}$, then it is good, otherwise, $\mbody$ is undefined in
    this case. The set $\{I\}$ implies that we will use the $m$ from $I$ without ambiguity. Moreover, we have to invoke $\mostSpecificOverride(m, I_d, I)$, to check if there are updated versions of $m$ between $I_d$ and $I$. Again we forbid ambiguity, so the expected set after pruning is also a singleton set $\{J\}$.
    \item Finally, we fetch the implementation of $m$ in interface $J$ and return its related information.
\end{itemize}
The definition of $\mtype$ used in typing rules simply relies on $\mbody$. In short,
$$\mbody(m, I, I) = (J, \overline{I_x}\ \overline{x}, I_e\ ?) \ \Longrightarrow\ \mtype(m, I) = \overline{I_x}\rightarrow I_e$$
